---
title: "Test Presentation"
author: "Nathalie Descusse-Brown"
date: "April 8, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE,warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output


<!-- ```{r gv, results="asis", cache=TRUE} -->
<!-- suppressPackageStartupMessages(library(googleVis)) -->
<!-- M <- gvisMotionChart(Fruits, "Fruit", "Year", -->
<!--                      options=list(width=600, height=400)) -->
<!-- print(M,"chart") -->
<!-- ``` -->

```{r multiplot,results="asis", cache=TRUE}
suppressPackageStartupMessages(library(googleVis))
G <- gvisGeoChart(Exports, "Country", "Profit",options=list(width=200, height=100))
T1 <- gvisTable(Exports,options=list(width=200, height=270))
M <- gvisMotionChart(Fruits, "Fruit", "Year", options=list(width=600, height=600))
GT <- gvisMerge(G,T1, horizontal=FALSE)
GTM <- gvisMerge(GT, M, horizontal=TRUE,tableOptions="bgcolor=\"#CCCCCC\" cellspacing=10")
```

```{r,dependson="multiplot",results="asis", cache=TRUE}
print(GTM,'chart')
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

